A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-17 6_2_printing_results.tex
lil change in print section titles

\revise{}{
\subsection{Printing results}
In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a. \emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.

@@

\subsubsection{Prints}
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
$f_0 = v_0 w_0 h $
with
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$
and
$h=\SI{0.1}{\milli\meter}$.
See \cref{back_pressure}.
The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
%
Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament.
The printing order is determined greadily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
The results can be viewed in \cref{prints}.

>>>>

\revise{}{
\subsection{Fabrication}
In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a. \emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.

@@

\subsubsection{Print results}
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
$f_0 = v_0 w_0 h $
with
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$
and
$h=\SI{0.1}{\milli\meter}$.
See \cref{back_pressure}.
The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
%
Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament.
The printing order is determined greadily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
The results can be viewed in \cref{prints}.
